Draft Exploration

### 2020-04-19 draft_exploration.Rmd
added positions from Lahman to master

>>>>

# Using Lahman Fielding dataset to collect player positions Grouped the data by
# player and found the mid career year to get an estimate for what their true
# position is. I then filtered each grouped player's data for their mid career
# year and the row of the position they played the most games at in that season
# (the table has a row for each position a player played each season). I then
# selected the playerID and POS columns to then join to the war dataset which
# contains matching player IDs. Unfortunately the Lahman table does not contain
# MLB IDs or matching player IDs so I need to go through the war table to match
# the player ID to the MLB ID.

fielding <- Fielding %>%
  group_by(playerID) %>%
  mutate(mid_career = round(((max(yearID) + min(yearID)) / 2), 0)) %>%
  filter(yearID == mid_career) %>%
  arrange(desc(G)) %>%
  slice(1) %>%
  select(playerID, POS)

# joining fielding to war to get mlb ID attached to position

war <- war %>%
  left_join(fielding, by = c("player_ID" = "playerID"))

# making war positions joinable to master by ensuring each MLB ID shows up only
# once. I grouped by mlb id and sliced a single row because all have the same
# position for a given player

war_positions <- war %>%
  group_by(mlb_ID) %>%
  slice(1) %>%
  select(mlb_ID, POS)

# Joining the war_positions table to master by mlb ID and renamed position

master <- master %>%
  left_join(war_positions, by = c("mlbid" = "mlb_ID")) %>%
  rename(position = POS)
